Spring haul-out behavior of seals in the Bering and Chukchi seas

### 2023-02-03 analysis/paper/London_HauloutBeahvior.Rmd
change data plot to geom_col
this was suggested by reviewer #1.

ggplot(data = seal_hours_tbl, aes(x = yday, y = 1, fill = n))+
        geom_tile()+
        scale_fill_gradientn(colors = rev(met.brewer("Hokusai2"))) +
        # scale_fill_viridis_c(option="mako") +
        scale_x_continuous(breaks = c(60, 91, 121, 152, 182),
                           labels = c("01 March", "01 April", "01 May", "01 June", "01 July"),
                           expand = expansion(mult = c(0, 0))) +
        scale_y_continuous(expand = expansion(mult = c(0, 0))) +
  guides(fill = guide_colorbar(title.position = "bottom", 
                               title.hjust = 0.5, barwidth = 15,
                               barheight = 0.5)) +
  facet_grid(species ~ .) + 
  theme(axis.text.x = element_text(hjust = 0),
        axis.text.y = element_blank(),
        axis.title = element_blank(),
        panel.grid = element_blank(),
        legend.position = "bottom") +
  labs(fill = "seal-hours of bio-logger data") +
  ggtitle("Density of haul-out behavior observations varies from March through July",
          subtitle = "data are grouped by day-of-year and presented in seal-hours collated across years (2005-2020)")

>>>>

ggplot(data = seal_hours_tbl, aes(x = yday, y = n, fill = n))+
  geom_col() +
        scale_fill_gradientn(colors = rev(met.brewer("Hokusai2"))) +
        # scale_fill_viridis_c(option="mako") +
        scale_x_continuous(breaks = c(60, 91, 121, 152, 182),
                           labels = c("01 March", "01 April", "01 May", "01 June", "01 July"),
                           expand = expansion(mult = c(0, 0))) +
        scale_y_continuous(expand = expansion(mult = c(0, 0))) +
  guides(fill = guide_colorbar(title.position = "bottom", 
                               title.hjust = 0.5, barwidth = 15,
                               barheight = 0.5)) +
  facet_grid(species ~ .) + 
  theme(axis.text.x = element_text(hjust = 0),
        axis.text.y = element_blank(),
        axis.title = element_blank(),
        panel.grid = element_blank(),
        legend.position = "bottom") +
  labs(fill = "seal-hours of bio-logger data") +
  ggtitle("Density of haul-out behavior observations varies from March through July",
          subtitle = "data are grouped by day-of-year and presented in seal-hours collated across years (2005-2020)")
